%==============================Abstract Page=================================================
\chapter*{\centerline{ABSTRACT}}
\addcontentsline{toc}{chapter}{ABSTRACT}
\thispagestyle{plain} 
% Abstract (200 to 250 Words)
\vspace{-0.5cm}
Recommendations systems are used everywhere from online shopping to movies to music. The project is a implementation of the best recommendation model among some generally used recommendation models tested thoroughly by introducing user-item data to it. The dataset used for testing is the Book Crossings Dataset which has been collected from Kaggle and has 1.1 million ratings of 230,000 books by 90,000 users. During testing, the most balanced model among the comparisions was found to be the kNN model. Scikit learn's NearestNeighbors model is a simple yet effective regression model that can be used for recommendations. After analysing, cleaning and formatting the dataset, it was fed into the model based on which the recommendations are generated. This model was compared against the Scikit learn's TruncatedSVD which is a Matrix Factorization model's Singular Value Decomposition model, Jaccard Similarity and a Dense Neural Network. During testing the kNN model was found to be quite goad at mainitaining good scores throughout the board with precision of 0.8045, recall of 0.7503 and F1-score of 0.7410. The other models though extremely better performing in one metric, lagged considerably in the other metrics.

\par
\textbf{Keywords:} \textit{Data Sparsity, Kaggle, K-Nearest Neighbors, Matrix Factorization, Recommendation Systems, Scikit learn, SVD.}
%=============================================================================================
% (a) Inclusion of three to four Keywords (Lexicographical Order)
\newpage