\chapter{FUTURE ENHANCEMENTS}

\section*{Content Based Recommendations}
The models that we've implemented are based on Collaboration based filtering, hence giving user-based recommendations. The project's scope can be broadened to include recommendation functions, suggesting items (e.g., books) based recommendations aka content based filtering to make the project's scope enter into realm of Hybrid filtering. The project can allocate resources to enhance feature engineering to derive valuable characteristics from the dataset items. A more comprehensive set of item attributes will enhance the accuracy of content-based recommendations. The webapp can be updated to offer users the flexibility to explore both collaborative and content-based recommendations, and collect their feedback to iteratively refine the user experience.

\section*{Search Filters}
The 'Book-Recommendation' web-app can incorporate advanced search filters into the 'Book-Recommendation' web application to facilitate users in refining their selections based on specific criteria. This feature becomes increasingly beneficial as the database expands, allowing users to efficiently navigate through a larger pool of options. These filters will empower users to refine their book selections based on diverse criteria, enhancing their browsing experience. This augmentation becomes particularly valuable as the database grows, offering users greater precision in finding books that align with their preferences and interests.

